Performance Optimization of Service Chain \\ for vCPE in Small Size Network \\ with OpenFlow Switch

### 2017-02-28 netsoft_paper.tex
citation fin

% Introduction
% First paragraph of paper need be big Alhabet
\section{Introduction}
\IEEEPARstart{S}{DN} has been developing almost a decade since the first Openflow article had be presented in 2008\cite{openflow-campus-network}. Openflow gives a brand new viewpoint on network research, and makes innovation on industries. This technic proposed not just a novel architecture but also bring out more methods of flexible traffic engineering. After tons of implementations and researches had been proposed, this architecture exposed some weakness in performance. The main concept of this architecture is separating data plane and control plane that put smart control and multi-path into real world. But legacy hardware design eventually put this perfect design into reality. To achieve high speed packet exchange, ternary content-addressable memory (TCAM) plays an important role in legacy fabric switching. This hardware design speed up the packet switching but it also cause high cost and less size problems.
In the beginning, most of SDN switch used legacy hardware design and just add software API support for temporary solution. The smaller TCAM size comes the less flow control rules but it can keep high performance in packet switching. It brings out inter-datacenter dynamic traffic routing because that scenario doesn’t need much flow entries.
At the same time as SDN was developed, Network Function Virtualization (NFV) has been introduced by Telco operators. Operators want to reduce their cost on maintaining old telco platform which may has been operated in 50 years. To replace the old platform with high maintenance cost, they use virtual machine (VM) based on new computers as solutions. This method can really save a lot of money in maintaining old platform but not all of operators have the same requirement as AT\&T; there is another idea about reducing OPEX and CAPEX in enterprise networks that is vCPE which was innovated by NEC. vCPE manage network functions on operation side to reduce cost which was deployed on cloud. Although both of technical ideas are perfect, it still address two critical problems. The first one is the lack of hardware support because these ideas need large size of tables to achieve multi VNF support. And the other is VM based on cloud may slow down the high speed etwork exchanging network.
From Pica-8 finished their first OpenFlow switched, there are so many implementation method on a SDN switch. Even Open Network Foundation (ONF) has a series of testing processes, it can’t shows completely testing result of SDN switch especially performance. Let us take flow entries as example, there are single table and multi table architectures much more based on hardware or software. Bandwidth control APIs have been an option in OpenFlow 1.3 but there are many switches still didn’t support these API. Even it did support, there are still at least two implementation methods should be noticed. Meters and per queue show different ways controlling bandwidth not mention to accuracy of bandwidth.
Service chain is another concept with vCPE framework because enterprise will apply a bulk of network services. This technic inherit weakness of SDN switches and vCPE so there is no standard to unified interface to link all services. It’s hard to combine and link all switches and cloud service in such complex situation. Different services on cloud must be working fine with different SDN switches and we believe that’s why most of service chain was implemented in VM on the cloud.

Therefore, the purpose of this paper can be summarized as follows:
\begin{enumerate}
\item To achieve extremely speed of packet exchanging of vCPE in small size network, this study proposed a mechanism to control OpenFlow tables which is in different hardware switches such as Lagopus, Pica-8 and Edgecore. It supports single table and multi-table implementation in different switches and sends status and information message to Ryu controller. This mechanism brings out a novel implementation method of VNF that combine hardware and software operations. It not only makes hardware usage more efficiency but also stays maximum flexibility in NFV deployment.

\item To cover most of NFV framework, this vCPE framework offer a multi cloud management feature. It can working with OpenDaylight on OpenStack and Ryu on Docker perfectly. Users can deploy their NFV features in any kind of VM system even in public cloud, and monitor it in same system.
\item To control flows with confidence, an application identification algorithm might be in consideration. The first thing comes out must be Intrusion Detection System (IDS) or Intrusion Prevention System (IPS) but there are 2 major weakness of this two kind of technic. The first is it spends a lot of time to identify connections, and network speed may hang on IPS. The other is it may can’t figure out encryption connections because not all of IDS or IPS have key matching feature. Most of modern cloud applications use https protocol as basic communication method which makes matter even worse. This study gives an algorithm to identify applications with statistical method with machine learning. The algorithm only use connection “attributes” to train an identification models such as packet direction, packet length. Afterward, the algorithm can identify network applications by this model. Even encryption connection can be identified with high accuracy because the algorithm monitor packet in statistical way instead of trying to decode it.
\item To analysis performance of this vCPE framework, this study integrate all of functions mention above to evaluate it even compare with the legacy network equipments.
This paper is structured as follows. Section II introduce the overall architecture of the framework what this study proposed. Section III describe multi table management mechanism in the beginning. Rest of section will show how to implement VNF with the mechanism. Section IV considers application identification in SDN because system can do nothing if the system doesn’t know what kind of application running on the network. Section V analytically performance of vCPE framework what we proposed include comparison with traditional network devices. Conclusion and future works will summary in the last section.
\end{enumerate}

@@

\subsection{Service Deployment Model}
Different from some related works are discussed about virtualizing network functions located in PE devices \cite{vcpe-enhance}, we come up with a network function service deployment model, with architecture mentioned in Fig. \ref{fig:desc_nfv_overview}. Because computing infrastructures handles the algorithm and policies, and the generic network devices only do stateless processing, the customer just need to buy a general SDN switch at their home gateway and will have a different network function service by subscribing different the NFV controller through our vCPE platform.

>>>>

% Introduction
% First paragraph of paper need be big Alhabet
\section{Introduction}
\IEEEPARstart{S}{DN}\cite{sdn-new-norm} has been developing almost a decade since the first Openflow article had be presented in 2008\cite{openflow-campus-network}. Openflow\cite{sp:openflow1.3} gives a brand new viewpoint on network research, and makes innovation on industries. This technic proposed not just a novel architecture but also bring out more methods of flexible traffic engineering. After tons of implementations and researches had been proposed, this architecture exposed some weakness in performance. The main concept of this architecture is separating data plane and control plane that put smart control and multi-path into real world. But legacy hardware design eventually put this perfect design into reality. To achieve high speed packet exchange, ternary content-addressable memory (TCAM) plays an important role in legacy fabric switching. This hardware design speed up the packet switching but it also cause high cost and less size problems.
In the beginning, most of SDN switch used legacy hardware design and just add software API support for temporary solution. The smaller TCAM size comes the less flow control rules but it can keep high performance in packet switching. It brings out inter-datacenter dynamic traffic routing because that scenario doesn’t need much flow entries.
At the same time as SDN was developed, Network Function Virtualization (NFV) \cite{nfvwp}\cite{laptop-sdn} has been introduced by Telco operators. Operators want to reduce their cost on maintaining old telco platform which may has been operated in 50 years. To replace the old platform with high maintenance cost, they use virtual machine (VM) based on new computers as solutions. This method can really save a lot of money in maintaining old platform but not all of operators have the same requirement as AT\&T; there is another idea about reducing OPEX and CAPEX in enterprise networks that is vCPE which was innovated by NEC\cite{nec-vcpe}. vCPE manage network functions on operation side to reduce cost which was deployed on cloud. Although both of technical ideas are perfect, it still address two critical problems. The first one is the lack of hardware support because these ideas need large size of tables to achieve multi VNF support. And the other is VM based on cloud may slow down the high speed network exchanging network \cite{nfv-placemet}, \cite{nfv-placement-model}.
From Pica8 \cite{pica8-switch} finished their first OpenFlow switches, there are so many implementation method on a SDN switch. Even Open Network Foundation (ONF)\ref{onf} has a series of testing processes, it can’t shows completely testing result of SDN switch especially performance. Let us take flow entries as example, there are single table and multi table architectures much more based on hardware or software. Bandwidth control APIs have been an option in OpenFlow 1.3 but there are many switches still didn’t support these API. Even it did support, there are still at least two implementation methods should be noticed. Meters and per queue show different ways controlling bandwidth not mention to accuracy of bandwidth.
Service chain \cite{service-chain} is another concept with vCPE framework because enterprise will apply a bulk of network services. This technic inherit weakness of SDN switches and vCPE so there is no standard to unified interface to link all services. It’s hard to combine and link all switches and cloud service in such complex situation. Different services on cloud must be working fine with different SDN switches and we believe that’s why most of service chain was implemented in VM on the cloud.

Therefore, the purpose of this paper can be summarized as follows:
\begin{enumerate}
\item To achieve extremely speed of packet exchanging of vCPE in small size network, this study proposed a mechanism to control OpenFlow tables which is in different hardware switches such as Lagopus, Pica8 and Edgecore. It supports single table and multi-table implementation in different switches and sends status and information message to Ryu controller. This mechanism brings out a novel implementation method of VNF that combine hardware and software operations. It not only makes hardware usage more efficiency but also stays maximum flexibility in NFV deployment.

\item To cover most of NFV framework, this vCPE framework offer a multi cloud management feature. It can working with OpenDaylight\cite{opendaylight} on OpenStack\cite{openstack} and Ryu\cite{web:ryu} on Docker\cite{docker} perfectly. Users can deploy their NFV features in any kind of VM system even in public cloud, and monitor it in same system.
\item To control flows with confidence, an application identification algorithm might be in consideration. The first thing comes out must be Intrusion Detection System (IDS) or Intrusion Prevention System (IPS) but there are 2 major weakness of this two kind of technic. The first is it spends a lot of time to identify connections, and network speed may hang on IPS. The other is it may can’t figure out encryption connections because not all of IDS or IPS have key matching feature. Most of modern cloud applications use https protocol as basic communication method which makes matter even worse. This study gives an algorithm to identify applications with statistical method with machine learning. The algorithm only use connection “attributes” to train an identification models such as packet direction, packet length. Afterward, the algorithm can identify network applications by this model. Even encryption connection can be identified with high accuracy because the algorithm monitor packet in statistical way instead of trying to decode it.
\item To analysis performance of this vCPE framework, this study integrate all of functions mention above to evaluate it even compare with the legacy network equipments.
\end{enumerate}

This paper is structured as follows. Section II introduce the overall architecture of the framework what this study proposed. Section III describe multi table management mechanism in the beginning. Rest of section will show how to implement VNF with the mechanism. Section IV considers application identification in SDN because system can do nothing if the system doesn’t know what kind of application running on the network. Section V analytically performance of vCPE framework what we proposed include comparison with traditional network devices. Conclusion and future works will summary in the last section.

@@

\subsection{Service Deployment Model}
Different from some related works are discussed about virtualizing network functions located in PE devices \cite{vcpe-enhance}, we come up with a network function service deployment model, with architecture mentioned in Fig. \ref{fig:desc_nfv_overview} based on the NetFATE (Network Function at the Edge) approach \cite{netfate}. Because computing infrastructures handles the algorithm and policies, and the generic network devices only do stateless processing, the customer just need to buy a general SDN switch at their home gateway and will have a different network function service by subscribing different the NFV controller through our vCPE platform.
